### 2019-08-22 Manuscripts/post-cogpsych/post-cogpsych.tex
Fixed last minute typos
Reorganised stimsteps -- now it is intialised when trialsets are initialised.

To our knowledge, no prior literature has yet explicitly discussed any empirical
effects of contrast in category generation. However, some evidence of contrast
can be seen in the data from Experiment 3 of cite{jern2013probabilistic}. We
leave a detailed analysis of this data to the supplemental materials.

@@

For the representativeness model, the single unbounded feature essentially
prevents the formation of edge effects along that feature. Consequently, this results in higher probabilities of the generating the first Beta exemplars along the edges of the bounded feature (Figure \ref{fig:e3-circles}c). As this
model does not explicitly recognize similarities as distances along the feature
space (unlike PACKER), it does not experience the compression in density regions
along the unbounded feature axis. Intuitively, this suggests that the
representativeness model (which prefers generating exemplars at the boundaries) will prefer to generate stimuli on the boundaries of the bounded feature with some amount of variance over unbounded feature.

@@

@@

\newpage
\section{Representativeness Model in Toroidal Space.}
\label{ap:wrapgauss}

>>>>

To our knowledge, no prior literature has yet explicitly discussed any empirical
effects of contrast in category generation. However, some evidence of contrast
can be seen in the data from Experiment 3 of \cite{jern2013probabilistic}. We
leave a detailed analysis of this data to the supplemental materials.

@@

The single unbounded feature prevents ... While the representativeness model
more closely resembles PACKER under this condition, note that the former still
more strongly predicts the generation of the first Betas exemplars at the
bounded edges compared to PACKER (Figure \ref{fig:e3-circles}c.) 
% For the representativeness model, the single unbounded feature essentially
% prevents the formation of edge effects along that feature. Consequently, this results in higher probabilities of the generating the first Beta exemplars along the edges of the bounded feature (Figure \ref{fig:e3-circles}c). As this
% model does not explicitly recognize similarities as distances along the feature
% space (unlike PACKER), it does not experience the compression in density regions
% along the unbounded feature axis. Intuitively, this suggests that the
% representativeness model (which prefers generating exemplars at the boundaries) will prefer to generate stimuli on the boundaries of the bounded feature with some amount of variance over unbounded feature.

@@

%Repeat hypotheses

@@

\newpage
\section{Representativeness Model in Toroidal Space}
\label{ap:wrapgauss}
